---
title: "Work Machine Learning"
author: "Bruce H"
date: "3/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Issues:

Many NA's
Many classes are "character" when they should be numeric.  Do these have any values?

Training and testing has same user names, so we should be trying to detect the user-specific characteristics.

```{r}
training <- read.csv("pml-training.csv", stringsAsFactors = FALSE)
testing <- read.csv("pml-testing.csv", stringsAsFactors = FALSE)
sort(unique(training$user_name))
sort(unique(testing$user_name))
```

results <- rfe(tr2m[,-c(1,54)],tr2m[,54], sizes = c(20:30), rfeControl = control)

> predictors(results)
 [1] "roll_belt"            "magnet_dumbbell_y"    "magnet_dumbbell_z"    "pitch_forearm"        "yaw_belt"            
 [6] "magnet_dumbbell_x"    "pitch_belt"           "roll_dumbbell"        "accel_dumbbell_y"     "roll_forearm"        
[11] "magnet_belt_z"        "accel_forearm_x"      "magnet_belt_y"        "gyros_belt_z"         "accel_belt_z"        
[16] "accel_dumbbell_z"     "yaw_dumbbell"         "magnet_arm_x"         "accel_dumbbell_x"     "roll_arm"            
[21] "magnet_forearm_z"     "accel_arm_x"          "total_accel_dumbbell" "accel_forearm_z"      "yaw_arm"             
[26] "magnet_belt_x"        "gyros_dumbbell_y"

> predictors(res3)
 [1] "roll_belt"            "magnet_dumbbell_z"    "magnet_dumbbell_y"    "pitch_forearm"        "yaw_belt"            
 [6] "roll_dumbbell"        "pitch_belt"           "accel_dumbbell_y"     "magnet_belt_y"        "roll_forearm"        
[11] "magnet_dumbbell_x"    "magnet_belt_z"        "accel_forearm_x"      "gyros_belt_z"         "roll_arm"            
[16] "accel_dumbbell_z"     "accel_belt_z"         "accel_dumbbell_x"     "magnet_forearm_z"     "yaw_dumbbell"        
[21] "gyros_dumbbell_y"     "magnet_forearm_y"     "yaw_arm"              "total_accel_dumbbell" "magnet_belt_x"       
[26] "accel_forearm_z"

> union(predictors(res3), predictors(results))
 [1] "roll_belt"            "magnet_dumbbell_z"    "magnet_dumbbell_y"    "pitch_forearm"        "yaw_belt"            
 [6] "roll_dumbbell"        "pitch_belt"           "accel_dumbbell_y"     "magnet_belt_y"        "roll_forearm"        
[11] "magnet_dumbbell_x"    "magnet_belt_z"        "accel_forearm_x"      "gyros_belt_z"         "roll_arm"            
[16] "accel_dumbbell_z"     "accel_belt_z"         "accel_dumbbell_x"     "magnet_forearm_z"     "yaw_dumbbell"        
[21] "gyros_dumbbell_y"     "magnet_forearm_y"     "yaw_arm"              "total_accel_dumbbell" "magnet_belt_x"       
[26] "accel_forearm_z"      "magnet_arm_x"         "accel_arm_x"

> intersect(predictors(res3), predictors(results))
 [1] "roll_belt"            "magnet_dumbbell_z"    "magnet_dumbbell_y"    "pitch_forearm"        "yaw_belt"            
 [6] "roll_dumbbell"        "pitch_belt"           "accel_dumbbell_y"     "magnet_belt_y"        "roll_forearm"        
[11] "magnet_dumbbell_x"    "magnet_belt_z"        "accel_forearm_x"      "gyros_belt_z"         "roll_arm"            
[16] "accel_dumbbell_z"     "accel_belt_z"         "accel_dumbbell_x"     "magnet_forearm_z"     "yaw_dumbbell"        
[21] "gyros_dumbbell_y"     "yaw_arm"              "total_accel_dumbbell" "magnet_belt_x"        "accel_forearm_z"


