---
title: "Work Machine Learning"
author: "Bruce H"
date: "3/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
RNGversion("3.6.0")
library(dplyr)
library(caret)
library(ggplot2)
library(randomForest)
```


Issues:

Many NA's
Many classes are "character" when they should be numeric.  Do these have any values?

```{r cache=TRUE}
training <- read.csv("pml-training.csv", stringsAsFactors = FALSE)
```

Training and testing has same user names, so we should be trying to detect the user-specific characteristics.

```{r}
testing <- read.csv("pml-testing.csv", stringsAsFactors = FALSE)
print(sort(unique(training$user_name)))
print(sort(unique(testing$user_name)))
```

Column selection and cleaning

```{r}
x <- lapply(training, class)
x1 <- x[x == "character"]

tr1 <- training
for (col1 in names(x1)[4:36]) {
    tr1[[col1]] <- as.numeric(tr1[[col1]])
}

# Get list of all with majority of NA's and remove

x2 <- numeric()
for (i in 1:dim(tr1)[2]) { if(mean(is.na(tr1[[i]])) > 0.5) x2 <- c(x2, i)}
tr2 <- select(tr1, -all_of(x2))

# Person Names are same in train and test, so we will keep those.

# Removing other columns

head(names(tr2),10)
tr2 <- select(tr2, -all_of(c(1, 3:7)))
head(names(tr2),10)

# We should have 54 left
dim(tr2)

# Take care of classe
tr2[,54] <- as.factor(tr2[,54])
```

Much smaller set for feature selection

```{r}
set.seed(1001)
minitrain <- createDataPartition(tr2$user_name, p=0.1, list=FALSE)
tr2m = tr2[minitrain,]
```

```{r feature_1, cache=TRUE}
# Using RFE to check which factors to use
# see https://machinelearningmastery.com/feature-selection-with-the-caret-r-package/

set.seed(1002)
control <- rfeControl(functions = rfFuncs, method="cv", number=10)
feature.time.1 <- system.time(results <- rfe(tr2m[,-c(1,54)],tr2m[,54], sizes = c(8:30), rfeControl = control))
```

```{r}
# predictors(results)
plot(results, type = c("g", "o"))
```

```{r feature_2, cache=TRUE}
# Recheck with another minitrain set

set.seed(1003)
minitrain3 <- createDataPartition(tr2$classe, p=0.1, list=FALSE)
tr3m = tr2[minitrain3,]
set.seed(1004)
feature.time.2 <- system.time(res3 <- rfe(tr3m[,-c(1,54)],tr3m[,54], sizes = c(8:30), rfeControl = control))
```

```{r cache=TRUE, warning=FALSE}
r2t <- data.frame(pred = predictors(results), rank = 1:length(predictors(results)))
r3t <- data.frame(pred = predictors(res3), rank = 1:length(predictors(res3)))
rtmatch <- inner_join(r2t, r3t, by = "pred")
rtmatch$rank <- rtmatch$rank.x + rtmatch$rank.y
rtmatch <- arrange(rtmatch, rank)
rtmatch$pred[1:15]
trnarrow <- select(training, all_of(rtmatch$pred[1:15]), classe)
trnarrow$classe <- as.factor(trnarrow$classe)
```

```{r train, cache=TRUE}
set.seed(1020)
timertr <- system.time(mrfn.t <- train(classe ~ ., trnarrow, method = "rf"))
```



```{r eval=FALSE, cache=TRUE}
set.seed(1010)
timerf <- system.time(mrfn <- randomForest(classe ~ ., data = trnarrow))
print(timerf)
```

The randomForest check took `r timerf`.




results <- rfe(tr2m[,-c(1,54)],tr2m[,54], sizes = c(20:30), rfeControl = control)

> predictors(results)
 [1] "roll_belt"            "magnet_dumbbell_y"    "magnet_dumbbell_z"    "pitch_forearm"        "yaw_belt"            
 [6] "magnet_dumbbell_x"    "pitch_belt"           "roll_dumbbell"        "accel_dumbbell_y"     "roll_forearm"        
[11] "magnet_belt_z"        "accel_forearm_x"      "magnet_belt_y"        "gyros_belt_z"         "accel_belt_z"        
[16] "accel_dumbbell_z"     "yaw_dumbbell"         "magnet_arm_x"         "accel_dumbbell_x"     "roll_arm"            
[21] "magnet_forearm_z"     "accel_arm_x"          "total_accel_dumbbell" "accel_forearm_z"      "yaw_arm"             
[26] "magnet_belt_x"        "gyros_dumbbell_y"

> predictors(res3)
 [1] "roll_belt"            "magnet_dumbbell_z"    "magnet_dumbbell_y"    "pitch_forearm"        "yaw_belt"            
 [6] "roll_dumbbell"        "pitch_belt"           "accel_dumbbell_y"     "magnet_belt_y"        "roll_forearm"        
[11] "magnet_dumbbell_x"    "magnet_belt_z"        "accel_forearm_x"      "gyros_belt_z"         "roll_arm"            
[16] "accel_dumbbell_z"     "accel_belt_z"         "accel_dumbbell_x"     "magnet_forearm_z"     "yaw_dumbbell"        
[21] "gyros_dumbbell_y"     "magnet_forearm_y"     "yaw_arm"              "total_accel_dumbbell" "magnet_belt_x"       
[26] "accel_forearm_z"

> union(predictors(res3), predictors(results))
 [1] "roll_belt"            "magnet_dumbbell_z"    "magnet_dumbbell_y"    "pitch_forearm"        "yaw_belt"            
 [6] "roll_dumbbell"        "pitch_belt"           "accel_dumbbell_y"     "magnet_belt_y"        "roll_forearm"        
[11] "magnet_dumbbell_x"    "magnet_belt_z"        "accel_forearm_x"      "gyros_belt_z"         "roll_arm"            
[16] "accel_dumbbell_z"     "accel_belt_z"         "accel_dumbbell_x"     "magnet_forearm_z"     "yaw_dumbbell"        
[21] "gyros_dumbbell_y"     "magnet_forearm_y"     "yaw_arm"              "total_accel_dumbbell" "magnet_belt_x"       
[26] "accel_forearm_z"      "magnet_arm_x"         "accel_arm_x"

> intersect(predictors(res3), predictors(results))
 [1] "roll_belt"            "magnet_dumbbell_z"    "magnet_dumbbell_y"    "pitch_forearm"        "yaw_belt"            
 [6] "roll_dumbbell"        "pitch_belt"           "accel_dumbbell_y"     "magnet_belt_y"        "roll_forearm"        
[11] "magnet_dumbbell_x"    "magnet_belt_z"        "accel_forearm_x"      "gyros_belt_z"         "roll_arm"            
[16] "accel_dumbbell_z"     "accel_belt_z"         "accel_dumbbell_x"     "magnet_forearm_z"     "yaw_dumbbell"        
[21] "gyros_dumbbell_y"     "yaw_arm"              "total_accel_dumbbell" "magnet_belt_x"        "accel_forearm_z"

trControl <- trainControl(method = "cv", number = 10)
system.time(mrfn.t <- train(classe ~ ., trnarrow, method = "rf", trControl = trControl))
   user  system elapsed 
 723.11   16.05  755.29

> mrfn.t
Random Forest 

19622 samples
   15 predictor
    5 classes: 'A', 'B', 'C', 'D', 'E' 

No pre-processing
Resampling: Cross-Validated (10 fold) 
Summary of sample sizes: 17661, 17659, 17659, 17659, 17661, 17661, ... 
Resampling results across tuning parameters:

  mtry  Accuracy   Kappa    
   2    0.9896544  0.9869146
   8    0.9904184  0.9878805
  15    0.9851689  0.9812416

Accuracy was used to select the optimal model using the largest value.
The final value used for the model was mtry = 8.

trControl <- trainControl(method = "repeatedcv", number = 10, repeats = 2)
system.time(mrfn.t3 <- train(classe ~ ., trnarrow, method = "rf", trControl = trControl))
   user  system elapsed 
1321.17   31.50 1369.76

> mrfn.t3
Random Forest 

19622 samples
   15 predictor
    5 classes: 'A', 'B', 'C', 'D', 'E' 

No pre-processing
Resampling: Cross-Validated (10 fold, repeated 2 times) 
Summary of sample sizes: 17659, 17661, 17661, 17659, 17659, 17660, ... 
Resampling results across tuning parameters:

  mtry  Accuracy   Kappa    
   2    0.9906230  0.9881389
   8    0.9904701  0.9879458
  15    0.9849408  0.9809527

Accuracy was used to select the optimal model using the largest value.
The final value used for the model was mtry = 2.

trnarrow.a <- trnarrow
trnarrow.a$user_name <- as.factor(training$user_name)
system.time(mrfn.t4 <- train(classe ~ ., trnarrow.a, method = "rf", trControl = trControl))
   user  system elapsed 
1668.78   33.37 1717.45 
> mrfn.t4
Random Forest 

19622 samples
   16 predictor
    5 classes: 'A', 'B', 'C', 'D', 'E' 

No pre-processing
Resampling: Cross-Validated (10 fold, repeated 2 times) 
Summary of sample sizes: 17661, 17660, 17659, 17660, 17659, 17660, ... 
Resampling results across tuning parameters:

  mtry  Accuracy   Kappa    
   2    0.9810926  0.9760793
  11    0.9905465  0.9880430
  20    0.9849658  0.9809854

Accuracy was used to select the optimal model using the largest value.
The final value used for the model was mtry = 11.


```{r train, cache=TRUE}
set.seed(1020)
trControl <- trainControl(method = "cv", number = 10)
timertr <- system.time(mrfn.t <- train(classe ~ ., trnarrow, method = "rf", trControl = trControl))
r1 <- mrfn.t$results
mtry.sel <- mrfn.t$bestTune[1]
acc1 <- round(r1[r1$mtry == as.character(mtry.sel),2], 4)
```


```{r}
fin1 <- mrfn.t$finalModel
cm1 <- fin1$confusion[,1:5]
tr.acc <- sum(diag(cm1)) / sum(cm1)
print(fin1$confusion)

```


